---
title: "Colocalisation report"
author: "[COLOC-reporter](https://github.com/ThomasPSpargo/COLOC-reporter)"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    
params:
  colocPriors: NULL
  coloc_abf_summary: NULL
  coloc_susie_summary: NULL
  abf.PP.plot: NULL
  abf.PP.plot.geneNear: NULL
  susie.PP.plots: NULL
  
---

<!---
Lines like the following are paired with matching lines including \\end{comment}, which selectively disable report sections based on conditions specified in inline R code
(c.f https://stackoverflow.com/questions/39550732/is-there-a-way-to-have-conditional-markdown-chunk-execution-in-rmarkdown)
`r if(is.null(params$example)) {"\\begin{comment}"}`
--->


```{r, include=FALSE}
library(kableExtra)
library(patchwork)
library(tidyverse)

knitr::opts_chunk$set(echo = FALSE,
                      warning= FALSE,
                      results = 'asis'
)

#reformat NA values as just a dash
options(knitr.kable.NA = '--',digits = 3)
```

___

`r if(is.null(params$coloc_abf_summary)) "\\begin{comment}"`

### coloc.abf analysis

This table overviews the results of colocalisation analysis across all sampled SNPs, under an assumption of at most one implicated variant per-trait. Analysis was performed with the priors `r paste(paste0(names(params$colocPriors$coloc.abf),"=",params$colocPriors$coloc.abf),collapse=", ")`. Documentation for `coloc.abf` can be viewed [here](https://chr1swallace.github.io/coloc/reference/coloc.abf.html).

``` {r, eval=!is.null(params$coloc_abf_summary)}

as.list(params$coloc_abf_summary) %>% data.frame(.) %>% mutate(across(matches("PP.H",.),~as.character(signif(.,3)))) %>%
  kable(.,align = "c",
        row.names=FALSE) %>%
  kable_styling(c("striped","hover"), full_width = F,fixed_thead = T) 

```


`r if(is.null(params$coloc_abf_summary)) "\\end{comment}"`

`r if(is.null(params$coloc_susie_summary)) "\\begin{comment}"`

### coloc.susie analysis

This table overviews the results of colocalisation `r ifelse(nrow(params$coloc_susie_summary)>1,"analyses across pairs of","analysis across")` credible sets identified during the fine-mapping step. Analysis was performed with the priors `r paste(paste0(names(params$colocPriors$coloc.susie),"=",params$colocPriors$coloc.susie),collapse=", ")`. Documentation for `coloc.susie` can be viewed [here](https://chr1swallace.github.io/coloc/reference/coloc.susie.html).

``` {r, eval=!is.null(params$coloc_susie_summary)}

params$coloc_susie_summary %>%
  mutate(across(matches("PP.H",.),~as.character(signif(.,3)))) %>%
  kable(.,align = "c",
        row.names=FALSE) %>%
  kable_styling(c("striped","hover"), full_width = F,fixed_thead = T) 

```

`r if(is.null(params$coloc_susie_summary)) "\\end{comment}"`

`r if(is.null(params$abf.PP.plot) && is.null(params$susie.PP.plots)) "\\begin{comment}"`

### SNP-wise posterior probability plots {.tabset}

Across these tabs are figures displaying per-SNP posterior probabilities for being a variant shared between traits. These posterior probabilities sum to 1 across all SNPs analysed and are predicated on the assumption that a shared variant exists; 95% credible SNPs are those spanned by the top 0.95 of posterior probabilities.

If any genes were found overlapping the base pair range spanned by the 95% credible SNPs ±10kb, then additional plots are returned displaying these overlaps. Further details on overlapping genes can be foind in the `tables` output directory.

NOTE: These plots are only returned for comparisons from coloc.abf or coloc.susie which show >0.2 posterior probability for the shared-variant hypothesis (PP.H4). However, this is an extremely lenient threshold and the results should be considered when H4 is more strongly supported.

`r if(is.null(params$abf.PP.plot) && is.null(params$susie.PP.plots)) "\\end{comment}"`

`r if(is.null(params$abf.PP.plot)) "\\begin{comment}"`

#### coloc.abf {.tabset}

##### All SNPs

```{r eval=!is.null(params$abf.PP.plot)}
params$abf.PP.plot
```

##### 95% credible SNPs with nearby genes

```{r eval=!is.null(params$abf.PP.plot.geneNear)}
params$abf.PP.plot.geneNear
```

`r if(is.null(params$abf.PP.plot)) "\\end{comment}"`

`r if(is.null(params$susie.PP.plots)) "\\begin{comment}"`

```{r, results='asis',eval=!is.null(params$susie.PP.plots), echo=FALSE}

#Declare the template for the dynamic tabs
template <- c(
    "\n\n#### coloc.susie row `r gsub('row','',names(params$susie.PP.plots)[{{num}}])` {.tabset}",
    "##### All SNPs",
    "```{r}",
    "params$susie.PP.plots[[{{num}}]]$ALLsnps",
    "```",
    "\n\n##### 95% credible SNPs with nearby genes",
    "```{r}",
    "params$susie.PP.plots[[{{num}}]]$snpsWgenes",
    "```"
    )


coloc.susiePlots <- lapply(seq_along(params$susie.PP.plots),
  function(num) knitr::knit_expand(text = template)
)

res<- knitr::knit(text = unlist(coloc.susiePlots),quiet=TRUE)
cat(res,sep="\n\n")

```

`r if(is.null(params$susie.PP.plots)) "\\end{comment}"`


<!--- Extra HTML to force removal of whitespace caused by the table of contents

<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>
--->

