---
title: "Workflow report"
author: "[COLOC-reporter](https://github.com/ThomasPSpargo/COLOC-reporter)"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    
params:
  P01: NULL
  P02: NULL
  P03: NULL
  rmdDir: NULL
  summaryFigures: NULL
---

_Please reach out to [Thomas Spargo](mailto:thomas.spargo@kcl.ac.uk) with any questions_

<!---
This document is a parent report used to concatenate across smaller report sections from this analysis workflow.

Each param of PO1..3 stores a list of parameters which are to be passed to the constituent child reports

P02 is a list with multiple reports derived for each trait. This chunk is therefore generated recursively.

rmdDir is the directory containing all child report template files

Parameterisation of child reports derived based on:
https://stackoverflow.com/questions/49475303/rmarkdown-child-documents-do-not-detect-their-params
--->

```{r, include=FALSE}
library(patchwork)
library(tidyverse)

options(knitr.duplicate.label = "allow")

knitr::opts_chunk$set(echo = FALSE,
                      warning= FALSE,
                      results = 'asis'
)

#Store the top-level parameters, since the params list will be replaced respectively to each child report
parentParams <- params 

#Remove the lock on the object 'params'
unlockBinding("params",env=environment())

```

`r if(is.null(parentParams$P01)) "\\begin{comment}"`

# Preprocessing

Placeholder

`r if(is.null(parentParams$P01)) "\\end{comment}"`

`r if(is.null(parentParams$P02)) "\\begin{comment}"`

# Finemapping

```{r, results='asis', echo=FALSE}

#Declare the template for the dynamic tabs; ie. the knitted report
template <- c(
    "\n\n## {{nm}}",
    "`r params <- parentParams$P02${{nm}}`",
    "```{r child=file.path(parentParams$rmdDir,'finemap_report.Rmd')}",
    "```")


report02 <- lapply(names(parentParams$P02),
  function(nm) knitr::knit_expand(text = template)
)

res<- knitr::knit(text = unlist(report02),quiet=TRUE)
cat(res,sep="\n\n")

```

`r if(is.null(parentParams$P02)) "\\end{comment}"`

`r if(is.null(parentParams$P03)) "\\begin{comment}"`

# Colocalisation analysis

Placeholder

`r if(is.null(parentParams$P03)) "\\end{comment}"`

___

`r if(is.null(parentParams$summaryFigures)) "\\begin{comment}"`

# SNP associations across traits {.tabset}

The following figures are comparable to the SNPwise plots displayed in the finemapping report summary, comparing additionally across a pair of traits.

```{r, eval=!is.null(parentParams$summaryFigures)}
#Eval is set because this chunk tries to execute even with the prior comment

#Save figs list and (for known columns) assign report-friendly names
figs <- readRDS(parentParams$summaryFigures)


recodes=c("p"="P-values",
          "z"="Z-score",
          "abs_z"="Absolute Z-score",
          "pip"="PIPs",
          "beta"="Beta coefficients")

names(figs) <- dplyr::recode(names(figs),!!!recodes)

#Patchwork wrap the plots
figs <- lapply(figs,function(x){
  wrap<- x$bpfigure / x$traitxy_figure+
    plot_layout(guides = 'collect',heights = c(1,2))
  
  return(wrap)
})

```


```{r}
#Declare the template for the dynamic tabs
template <- c(
  "\n\n## {{names}}",
  "```{r, fig.height=8, fig.width=8}",
  "figs[[{{num}}]]",
  "```")

tabs <- mapply(function(num,names) knitr::knit_expand(text = template),
               num=seq_along(figs),names=names(figs))

res<- knitr::knit(text = unlist(tabs),quiet=TRUE)
cat(res,sep="\n\n")
```


`r if(is.null(parentParams$summaryFigures)) "\\end{comment}"`

___

