---
title: "Preprocessing report"
author: "[COLOC-reporter](https://github.com/ThomasPSpargo/COLOC-reporter)"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    
params:
  saveopts: NULL
  traits: NULL
  target_region: NULL
  initial_data_overview: NULL
  ref_harmonised_data_overview: NULL
  final_data_overview: NULL
  
---

<!---
Lines like the following are paired with matching lines including \\end{comment}, which selectively disable report sections based on conditions specified in inline R code
(c.f https://stackoverflow.com/questions/39550732/is-there-a-way-to-have-conditional-markdown-chunk-execution-in-rmarkdown)
`r if(is.null(params$example)) {"\\begin{comment}"}`
--->


```{r, include=FALSE}
library(kableExtra)
library(tidyverse)

knitr::opts_chunk$set(echo = FALSE,
                      warning= FALSE,
                      results = 'asis'
)

#reformat NA values as just a dash
options(knitr.kable.NA = '--',digits = 3)

#Preprocessing data table names
prettyHeader<- c("Traits","Total","p<5e-8",#"N SNPs p <5e-8",
                 "Value","SNP ID","Value","SNP ID")
prettyHeaderAbove<-c(" "=1,"Number of SNPs"=2,"Smallest p-value" = 2, "Largest absolute beta" = 2)

```

___

### Preprocessing summary {.tabset}

<details><summary>View options set</summary>

```{r}

enframe(params$saveopts) %>% 
  mutate(value=as.character(value),
         name=paste0("-- -- ",name)) %>%
  rename(Option=name,`Current setting`=value) %>%
kable(.,align = "c",
      row.names=FALSE) %>%
kable_styling(c("striped","hover"), full_width = F,fixed_thead = T) %>%
scroll_box(width = "100%", height = "400px")

```

</details>

<br>

Analysis will be performed for the traits `r paste(params$traits, collapse=", ")` in the genomic region `r params$target_region`.

The following tables provide a quick overview of the data available in the region before any processing, after harmonising with the reference, and after harmonising across the analysed traits.

`r if(is.null(params$initial_data_overview)) "\\begin{comment}"`


#### Initial data

``` {r, eval=!is.null(params$initial_data_overview)}

overview<- params$initial_data_overview

overview$p_min <- as.character(signif(overview$p_min,3))

kable(overview,align = "c", row.names=FALSE,col.names =prettyHeader) %>%
  kable_styling(c("striped","hover"), full_width = F,fixed_thead = T) %>%
  add_header_above(prettyHeaderAbove)

```

`r if(is.null(params$initial_data_overview)) "\\end{comment}"`

`r if(is.null(params$ref_harmonised_data_overview)) "\\begin{comment}"`

#### Harmonised with reference

``` {r, eval=!is.null(params$ref_harmonised_data_overview)}

overview<- params$ref_harmonised_data_overview

overview$p_min <- as.character(signif(overview$p_min,3))

kable(overview,align = "c", row.names=FALSE,col.names =prettyHeader) %>%
  kable_styling(c("striped","hover"), full_width = F,fixed_thead = T) %>%
  add_header_above(prettyHeaderAbove)

```

`r if(is.null(params$ref_harmonised_data_overview)) "\\end{comment}"`

`r if(is.null(params$final_data_overview)) "\\begin{comment}"`

#### Harmonised across traits

``` {r, eval=!is.null(params$final_data_overview)}

overview<- params$final_data_overview

overview$p_min <- as.character(signif(overview$p_min,3))

kable(overview,align = "c", row.names=FALSE,col.names =prettyHeader) %>%
  kable_styling(c("striped","hover"), full_width = F,fixed_thead = T) %>%
  add_header_above(prettyHeaderAbove)

```

`r if(is.null(params$final_data_overview)) "\\end{comment}"`

<!--- Extra HTML to force removal of whitespace caused by the table of contents --->

<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>
